\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\section*{Applied Econometrics II-Lab}

In the labor market for married women, wages and hours of work are jointly determined by labor supply and labor demand. Consider the following structural model:

\subsection*{Labor Supply (LS)}

\begin{equation}
hrs_i = \beta_0 + \beta_1 \, lwage_i + \beta_2 \, educ_i + \beta_3 \, age_i + \beta_4 \, kidslt6_i + \beta_5 \, nwifeinc_i + u_i
\end{equation}

\subsection*{Labor Demand (LD)}

\begin{equation}
lwage_i = \gamma_0 + \gamma_1 \, hrs_i + \gamma_2 \, educ_i + \gamma_3 \, exper_i + \gamma_4 \, exper_i^2 + v_i
\end{equation}

\subsection*{Variable Definitions}

\begin{itemize}
  \item $hrs$: Annual hours worked  
  \item $lwage$: Log of hourly wage  
  \item $educ$: Years of education  
  \item $age$: Woman’s age  
  \item $kidslt6$: Number of children under 6  
  \item $nwifeinc$: Husband’s income  
  \item $exper$: Labor market experience  
\end{itemize}
\begin{enumerate}
    \item Explain why $lwage$ is endogenous in the labor supply equation.
    \item Explain why $hrs$ is endogenous in the labor demand equation.
    \item What happens if both equations are estimated using Ordinary Least Squares (OLS)?





    \item Which variables can be used as instruments for $lwage$ in the labor supply equation?
    \item Which variables can be used as instruments for $hrs$ in the labor demand equation?
    \item Explain why these instruments are valid. Your answer should discuss both \textit{relevance} and \textit{exogeneity}.




Using the Mroz dataset from Wooldridge, do the following:


    \item Estimate the labor supply equation using OLS.
    \item Estimate the labor demand equation using OLS.
    \item Estimate both equations using Two-Stage Least Squares (2SLS).
    \item Compare the OLS and IV estimates of:
    \begin{itemize}
        \item the wage effect on hours,
        \item the hours effect on wages.
    \end{itemize}
\end{enumerate}

\end{document}
